Lyman-alpha spectra from rotating outflows

### 2017-11-03 paper/paper.tex
new plot theta

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the 
valley for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity} 
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=75$\kms and rotation velocity of $\vrot=50$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/valley_intensity}
	\end{center}
	\caption{\textbf{Caption:} We fixed $\vout=75$\kms and $\vrot=50$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

Regarding de Doppler shift... By this logic then, the quality and accuracy of 
the spectrum, obtained by a Doppler shift, increases with the optical depth \tauh. 
This because the more \tauh, the more anisotropic is the photons' distribution 
at the galaxy's border.

The introduction of rotation in the model implies that it will only affect 
galaxies with its viewing angle

>>>>

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the 
valley between peaks, for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity} 
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=75$\kms and rotation velocity of $\vrot=50$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/valley_intensity}
	\end{center}
	\caption{\textbf{Caption:} We fixed $\vout=75$\kms and $\vrot=50$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

Regarding de Doppler shift... Then, the quality and accuracy of 
the spectrum, obtained by a Doppler shift, increases with the optical depth \tauh. 
This is because the more \tauh, the more anisotropic is the photons' distribution 
at the galaxy's border.

The introduction of rotation in the model implies that it will only affect 
galaxies with its viewing angle...
